---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dear Participants,

We are so excited that you will be joining our tutorial "Graphing multivariate categorical data: The how, what and why of mosaic plots and alluvial diagrams" on Wednesday, July 7 from 7:45pm-10:15pm UTC.

In order to get the most out of the workshop, please install the following or update to the latest version in advance.

**ggalluvial** (0.12.3)  

**RColorBrewer** (1.1-2)  

**tidyverse** (1.3.0)  

**vcd** (1.4-8)  

Next please run the following code examples to make sure the above packages are working. The graphs shown below should appear.

```{r, fig.width=5, fig.height=3}
library(vcd)
mosaic(Titanic)
mosaic(HairEyeColor)
```


```{r, fig.width=5, fig.height=3}
library(tidyverse)
library(ggalluvial)
ggplot(as.data.frame(Titanic),
       aes(y = Freq,
           axis1 = Class, axis2 = Sex, axis3 = Age,
           fill = Survived)) +
  geom_alluvium() +
  scale_x_discrete(limits = c("Class", "Sex", "Age"))
```

Tutorial materials will be added soon to: https://github.com/jtr13/graphcat

Don't hesitate to contact us in advance if you have any questions:

Joyce Robbins jtr13@columbia.edu

Ludmila Janda  ludmila.janda@gmail.com

Enjoy the conference!

best,
Joyce and Ludmila
