---
title: "Graphing Multivariate Categorical Data Lab"
date: "7/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Congress

This dataset contains information about the members of the U.S. Congress: both in the Senate (`type==Senate`) and House of Representatives (`type==House`). 

Original data source: `legislators-current.csv`   https://github.com/unitedstates/congress-legislators

Data processing script: https://github.com/jtr13/graphcat/blob/main/R/read_congress.R

```{r}
congress <- readr::read_csv("https://raw.githubusercontent.com/jtr13/graphcat/main/data/congress.csv")
```

Explore relationships among `gender`, `party`, `type` (House or Senate) and `age` (in decades: `20s` through `80s`)

Start small, that is, one variable at a time, and build up to using three or all four variables. 

Think about the order of the variables, the direction of the cuts, and the order of factor levels.

Remember, the dependent variable should be the last cut and it should be horizontal.



# Birth Data

1. Load the birth_data.csv file 
2. Make an alluvial diagram 
3. Pick a color scheme 

Variables
`user_id`: randomly generated user id        
`pre_weight`: weight of mother before pregnancy      
`pre_weight_cat`: weight of mother before pregnancy split into quartiles  
`weight_gain`: weight gain of mother during pregnancy        
`weight_gain_cat`: weight gain of mother during pregnancy split into quartiles   
`mother_age`: mother's age at start of pregnancy

```{r}
birth_data <- readr::read_csv("https://raw.githubusercontent.com/jtr13/graphcat/main/data/birth_data_alluvial.csv")
```
